Learning the local coding scheme: Jointly Optimized Locally Linear Classifiers

### 2017-09-11 paper/llncs2e/PKDD2017.tex
reconstruct code
add test routine

			Banana 		   	& 3533 & 1767 & 2 & 2  \\

@@

			W8a           	& 49479 & 14951 & 300 & 2  \\

@@

	\begin{table}
		\begin{tabu} to \textwidth {|X[c]| X[c]| X[c]| X[c]| X[c]|}
			\hline
			Banana              & Train loss & Test loss & Acc(\%) &test time \\
			\hline
			\textbf{SVM} 		   	&0.9061$\pm$0.0000  &0.8958$\pm$0.0018  & 55.40 $\pm$ 0.00 & $\times$1  \\ \hline
			\textbf{LLSVM}     		&0.3139$\pm$0.0027  &0.2547$\pm$0.0042  & 89.16 $\pm$ 0.13 & $\times$12.06 \\ \hline
			\textbf{LLC-SAPL}       &0.2930$\pm$0.0019  &0.2307$\pm$0.0050  & \textbf{90.03 $\pm$ 0.31} &$\times$11.95 \\ \hline
			\textbf{LLC-JO}         &\textbf{0.2416$\pm$0.0016}  &\textbf{0.2103$\pm$0.0034}  & \textbf{90.03 $\pm$ 0.34} &$\times$11.05 \\ \hline
			\hline
			Magic04              & Train loss & Test loss & Acc(\%) &test time \\
			\hline
			\textbf{SVM} 		   	&0.4874$\pm$0.0005  &0.5022$\pm$0.0020  &78.35 $\pm$ 0.46  &$\times$1 \\ \hline
			\textbf{LLSVM}     		&0.4105$\pm$0.0019  &0.4017$\pm$0.0102  &82.97 $\pm$ 0.42  &$\times$21.56 \\ \hline
			\textbf{LLC-SAPL}       &0.3604$\pm$0.0019  &0.3720$\pm$0.0057  &83.18 $\pm$ 0.29  &$\times$22.04 \\ \hline
			\textbf{LLC-JO}         &\textbf{0.3390$\pm$0.0017}  &\textbf{0.3422$\pm$0.0038}  &\textbf{83.53 $\pm$ 0.28}   &$\times$22.92\\ \hline
			\hline
			IJCNN              & Train loss & Test loss & Acc(\%) &test time\\
			\hline
			\textbf{SVM} 		   	&0.1930$\pm$0.0000  &0.1896$\pm$0.0000  & 90.50 $\pm$ 0.00  &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.1072$\pm$0.0014  &0.0947$\pm$0.0009  & 96.18 $\pm$ 0.25  &$\times$15.52\\ \hline
			\textbf{LLC-SAPL}       &0.0970$\pm$0.0027  &0.0858$\pm$0.0200  & 96.97 $\pm$ 0.68  &$\times$15.78\\ \hline
			\textbf{LLC-JO}         &\textbf{0.0942$\pm$0.0007}  &\textbf{0.0716$\pm$0.0074}  & \textbf{97.12 $\pm$ 0.51}   &$\times$16.30\\ \hline
				\hline
				W8a              & Train loss & Test loss & Acc(\%) &test time\\
				\hline
				\textbf{SVM} 		   	&0.0409$\pm$0.0001  &0.0415$\pm$0.0000  &98.15 $\pm$ 0.02  &$\times$1 \\ \hline
				\textbf{LLSVM}     		&0.0319$\pm$0.0002  &0.0275$\pm$0.0004  &98.82 $\pm$ 0.04  &$\times$7.08 \\ \hline
				\textbf{LLC-SAPL}       &0.0268$\pm$0.0002  &0.0201$\pm$0.0003  &99.03 $\pm$ 0.03 &$\times$7.17  \\ \hline
				\textbf{LLC-JO}         &\textbf{0.0258$\pm$0.0007}  &\textbf{0.0194$\pm$0.0008}  &\textbf{99.08 $\pm$ 0.02}  &$\times$7.28 \\ \hline
		\end{tabu}
		\caption{Comparison of different algorithms in terms of train loss, test loss, classification accuracy and test time (normalized to test time of SVM)}
	\end{table}

>>>>

			phishing 		   	& 7370 		& 3685 		& 68 	& 2  \\

@@

			w8a           		& 49749 	& 14951 	& 300 	& 2  \\
			connect-4           & 40740 	& 20368 	& 126 	& 2  \\
			Covtype           	& 387342 	& 193670 	& 54 	& 2  \\

@@

			phishing              & Train loss & Test loss & Acc(\%) &test time \\
			\textbf{SVM} 		   	&0.1826$\pm$0.0002  &0.1964$\pm$0.0006  & 92.24 $\pm$ 0.10 & $\times$1  \\ \hline
			\textbf{LLSVM}     		&0.1688$\pm$0.0027  &0.1861$\pm$0.0042  & 92.66 $\pm$ 0.23 & $\times$8.91 \\ \hline
			\textbf{LLC-SAPL}       &0.1385$\pm$0.0011  &0.1509$\pm$0.0026  & 93.92 $\pm$ 0.18 & $\times$9.27 \\ \hline
			\textbf{LLC-JO}         &0.0580$\pm$0.0016  &0.1026$\pm$0.0026  & 95.66 $\pm$ 0.17 & $\times$8.66 \\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0487$\pm$0.0020}  &\textbf{0.0965$\pm$0.0040}  & \textbf{95.84 $\pm$ 0.34} &$\times$8.91 \\ \hline
			Magic04              & Train loss & Test loss & Acc(\%) &test time \\
			\textbf{SVM} 		   	&0.4810$\pm$0.0002  &0.5004$\pm$0.0014  &78.33 $\pm$ 0.13  &$\times$1 \\ \hline
			\textbf{LLSVM}     		&0.4022$\pm$0.0018  &0.4289$\pm$0.0016  &79.57 $\pm$ 0.30  &$\times$21.56 \\ \hline
			\textbf{LLC-SAPL}       &0.3670$\pm$0.0019  &0.3923$\pm$0.0031  &81.60 $\pm$ 0.18  &$\times$22.04 \\ \hline
			\textbf{LLC-JO}         &0.3025$\pm$0.0010  &0.3339$\pm$0.0017  &84.88 $\pm$ 0.36  &$\times$22.92\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.2852$\pm$0.0008}  &\textbf{0.3238$\pm$0.0029}  &\textbf{85.14 $\pm$ 0.44}   &$\times$22.92\\ \hline
			IJCNN              & Train loss & Test loss & Acc(\%) &test time\\
			\textbf{SVM} 		   	&0.1827$\pm$0.0000  &0.1863$\pm$0.0000  & 90.50 $\pm$ 0.00  &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.1081$\pm$0.0028  &0.1130$\pm$0.0039  & 94.51 $\pm$ 0.30  &$\times$15.52\\ \hline
			\textbf{LLC-SAPL}       &0.1002$\pm$0.0017  &0.1054$\pm$0.0015  & 95.17 $\pm$ 0.21  &$\times$15.78\\ \hline
			\textbf{LLC-JO}         &0.0703$\pm$0.0002  &0.0683$\pm$0.0024  & 97.66 $\pm$ 0.11  &$\times$16.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0550$\pm$0.0007}  &\textbf{0.0584$\pm$0.0018}  &\textbf{98.26 $\pm$ 0.12}   &$\times$15.42\\ \hline
			w8a              & Train loss & Test loss & Acc(\%) &test time\\
			\textbf{SVM} 		   	&0.0552$\pm$0.0001  &0.0567$\pm$0.0003  & 97.07 $\pm$ 0.00  &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.0320$\pm$0.0014  &0.0333$\pm$0.0019  & 98.45 $\pm$ 0.25  &$\times$11.72\\ \hline
			\textbf{LLC-SAPL}       &0.0262$\pm$0.0007  &0.0274$\pm$0.0005  & 98.74 $\pm$ 0.18  &$\times$12.78\\ \hline
			\textbf{LLC-JO}         &0.0250$\pm$0.0003  &0.0262$\pm$0.0004  & 98.74 $\pm$ 0.07  &$\times$9.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0213$\pm$0.0016}  &\textbf{0.0228$\pm$0.0028}  &\textbf{98.96 $\pm$ 0.31}   &$\times$9.92\\ \hline
			connect-4              & Train loss & Test loss & Acc(\%) &test time\\
			\textbf{SVM} 		   	&0.4268$\pm$0.0002  &0.4257$\pm$0.0008  & 81.50 $\pm$ 0.12  &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.2998$\pm$0.0017  &0.3196$\pm$0.0021  & 87.30 $\pm$ 0.25  &$\times$7.52\\ \hline
			\textbf{LLC-SAPL}       &0.2626$\pm$0.0007  &0.2901$\pm$0.0013  & 88.19 $\pm$ 0.15  &$\times$8.78\\ \hline
			\textbf{LLC-JO}         &0.2180$\pm$0.0025  &0.2663$\pm$0.0030  & 89.15 $\pm$ 0.23  &$\times$9.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.1496$\pm$0.0017}  &\textbf{0.2225$\pm$0.0020}  &\textbf{90.94 $\pm$ 0.21}   &$\times$9.92\\ \hline
			Covtype              & Train loss & Test loss & Acc(\%) &test time\\
			\textbf{SVM} 		   	&0.0409$\pm$0.0001  &0.0415$\pm$0.0000  &98.15 $\pm$ 0.02  &$\times$1 \\ \hline
			\textbf{LLSVM}     		&0.0319$\pm$0.0002  &0.0275$\pm$0.0004  &98.82 $\pm$ 0.04  &$\times$7.08 \\ \hline
			\textbf{LLC-SAPL}       &0.0268$\pm$0.0002  &0.0201$\pm$0.0003  &99.03 $\pm$ 0.03 &$\times$7.17  \\ \hline
			\textbf{LLC-JO}         &\textbf{0.0258$\pm$0.0007}  &\textbf{0.0194$\pm$0.0008}  &\textbf{99.08 $\pm$ 0.02}  &$\times$7.28 \\ \hline
		\caption{Comparison of different algorithms in terms of train loss, test loss, classification accuracy and test time (normalized to test time of SVM)}
